---
title: "homepage"
author: "wz2631"
date: "2022-11-23"
output: html_document
---

```{r,echo=FALSE}
library(shiny)
```

```{r,echo=FALSE}
shinyUI(fluidPage(
  titlePanel("title panel"),
  sidebarLayout(
  sidebarPanel( "sidebar panel"),
  mainPanel("main panel")
  )))
```

```{r,echo=FALSE}
ui <- fluidPage(
h1("Did you sleep well?"),
h2("Sleep problems are common"),
h3("Sleep & health"),
h4("Sleep & public health"),
h5("And here is our project! "),
hr(),
br(),
p(strong("bold")),
p(em("italic")),
p(code("code")),
p("Click",span(style = "color:blue","Here")),
  a(herf = "www,http://rstudio.com","RStudio Home ")
)
```

Adults should sleep 7 or more hours per night on a regular basis to promote optimal health[1]. However, more than one-third of the US population gets less than the recommended amount of sleep (https://aasm.org/seven-or-more-hours-of-sleep-per-night-a-health-necessity-for-adults/). 
Not getting enough sleep is linked with chronic diseases and adverse health conditions[1], threateniing the nation’s overall public health. Short sleep duration along with other dimensions of poor sleep has been associated with weight gain and obesity[2], type 2 diabetes[3],  increased risk of hypertension[4], cardiovascular disease[5] and depression[6, 7]. Sleep deprivation and disorders are also associated with impaired immune function[8], chronic pain[9], impaired performance, increased errors, and greater risk of accidents[10].

